---
title: 'STAT 441: Midterm 2'
author: "NAME HERE"
date: "DATE"
output: pdf_document
---

## Application in R: Cereal

For this part of the exam you will need to use the cereal dataset from Lock5’s Statistics: Unlocking the power of data.  These data are available on the Lock5 website.  

#### Citations: 

* Lock, R. H., Lock, P. F., Morgan, K. L., Lock, E. F., & Lock, D. F. (2025). Statistics: Unlocking the power of data. John Wiley & Sons.
* https://www.lock5stat.com/datapage3e.html (Accessed Nov 3, 2025)

#### Description of Data:

These data contain nutritional information for 30 observations of different cereal types.


### Access the Data

```{r}
# IMPORT THE DATA
cereal<-read.delim("https://www.lock5stat.com/datasets1e/Cereal.txt",
                   header=TRUE)

str(cereal)
```

### Part A: Pairs Plot

#### (i) Create a pairs plot for Calories, Sugar, Fat, Protein, and Carbs.  

```{r}
## INSERT CODE HERE ###
```

#### (ii) Discuss if there are linear relationships between Calories and the explanatory variables (Sugar, Fat, Protein, and Carbs).  

YOUR ANSWER HERE: 

#### (iii) How is evaluating this (linear) property fundamental in multiple linear regression (MLR)? 


YOUR ANSWER HERE: 



### Part B: 3D Scatter Plot with Fitted Model

#### (i) Since we can’t see in more than three dimensions, let’s limit the explanatory variables to Sugar and Fat.  Fit an MLR model, for Calories as a function of Sugar and Fat. 

```{r}
### INSERT CODE HERE
```

#### (ii) Make a 3D scatterplot with the least squares fitted plane. 

```{r}
### INSERT CODE HERE
```


### Part C: Predict

Professor Smalley noticed that Frosted Flakes are not contained in these data.  This is her father’s favorite cereal.  According to Google (citing USDA), a one cup serving of Frosted Flakes has 0.7 grams of fat and 11 grams of sugar.  

Use your model from Part B (with Sugar and Fat) to predict the amount of calories from a new observation not contained in the data. 

#### (i) What is the point estimate? 

```{r}
### INSERT CODE HERE ###
```

#### (ii) Provide an appropriate 95% interval for this estimate?  Please explain why you chose the interval method that you did.

```{r}
### INSERT CODE HERE ###
```

YOUR EXPLANATION HERE: 

### Part D: Quadratic Forms and ANOVA

Construct the ANOVA table using quadratic forms.

```{r}
## INSERT CODE HERE ##
```


### Part E: Global Model 

Test for significance of regression using an F test.  Please use a 5% significance level.

#### (i) Write the null and alternative hypotheses for the global model

YOUR ANSWER HERE: 

#### (ii) Write a five part conclusion for the global F-test.

YOUR ANSWER HERE:


