---
title: 'FALL 2025 DATA151: Midterm #1 (R Section)'
author: "CRAYON CODE NAME"
date: "TODAYS DATE"
output: pdf_document
---
  

### Throwing Shade!

Please read ALL descriptions and directions. 

#### Description: 

Researchers are interested in studying the effect of shade, during certain times of the growth season on kiwi crop yield. 
  
#### Part 0: Directions

* Create a new R markdown document for the Midterm template 
* Create a folder called "MIDTERM_1"
* Save new Rmd in your R Studio Cloud as "data151_mid1_COLOR"

#### Part 1: Getting Started (5 points)
* Change the author to your code name and date in the heading of the R markdown - 2 points
* Leave yourself at least 3 comments in your code chunks (overall) - 3 points

#### Part 2: Installing the package  (2.5 points)

In order to access these data you will need to install the package `DAAG`.

```{r}
## INSERT CODE HERE ###

```

#### Part 3: Library (2.5 points)

Now you actually need to call the library for the DAAG package to be able to get the data.  

```{r}
## INSERT CODE HERE ###

```

#### Part 4: Bring the Data into the Global Environment (2.5 points)

These data are simply called `kiwishade`.  Please call them into the global environment

```{r}
## INSERT CODE HERE ###

```

#### Part 5: Learn about the Data (5 points)

Look at the help file and read about this study. 

```{r}
## INSERT CODE HERE ###
```


After reading about this study answer the following question. 

Do these data come from an observational study or an experiment?  Explain your choice. 

```{}
YOUR ANSWER HERE: 
```


#### Part 6: Structure 

##### A) (2.5 points) Look at the structure of your data.  

How many observations are there? 
  
```{r}
## INSERT CODE HERE ###

```

##### B) (2.5 points) Look at the first six rows of the data frame.  
  
NOTE: You must write code with the proper function for this.

```{r}
## INSERT CODE HERE ###
```

Are these data tidy?  Why or why not? 

```{}
YOUR ANSWER HERE:

```


#### Part 7: Understanding the study 


##### A): What is the response variable? (2.5 points)

```{}
YOUR ANSWER HERE: 

```

##### B): What is the explanatory variable? (2.5 points)

```{}
YOUR ANSWER HERE: 

```

Is there a control in this study?  What is it?

```{}
YOUR ANSWER HERE: 

```


#### Part 8: Make a hypothesis (2.5 points)

Write a hypothesis about how you think the treatments might effect the response.


```{}
YOUR ANSWER HERE: 

```

#### Part 9: Visualize (2.5 points)

Explore the relationship between the response and explanatory by creating a boxplot.  

HINT: Please look at your class notes from OrchardSprays and ToothGrowth.

```{r}
## MAKE SURE TO LABEL YOUR AXES
## INSERT CODE HERE ###

## INSERT CODE HERE ###
```

#### Part 10: Observations (2.5 points)

What are your observations from this plot? Does your hypothesis (from Part 8) appear to be supported? Explain.

```{}
YOUR ANSWER HERE: 

```

#### EXTRA CREDIT (5 points)

Explain how blocking is used in this study.

Hint: Read the details.

```{}
YOUR ANSWER HERE
```

